TO FIND

### 2013-05-01 ms.tex
File upload

%--------------------------------
section{Introduction}

- Contribution of neutral theory to ecology: the recognition of the importance of dispersal in structuring communities. The provision of a

@@

- Objective of the paper 
	- Already several reviews of neutral theory in the literature
	- We will use this opportunity to explore in more details the contribution of neutral theory to our understanding of metacommunities
	- We will pay a particular attention to recent developments at the crossroad of network theory
	- Move from a perspective where dispersal is either global or spatially explicity (e.g. over a lattice), and spatial constant, to a perspective focusing on the variance of dispersal. 
	- More specifically, the objective of the paper is to use neutral theory to better reveal the importance of landscape network structure on the distribution of diversity.
	- Referred as a "spatial contingency" 
	- Relevance to limnology

@@

%--------------------------------
section{Network representation of landscapes}

@@

%--------------------------------
section{Model description}

For each model:
	- description of the dynamics
	- description of the algorithm
	- main predictions

%--------------------------------
section{Results}

- Alpha diversity
- Beta diversity

%--------------------------------
section{Conclusion}

>>>>

\documentclass[letterpaper,twocolumn,showkeys]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}

\begin{document}

\title{TO FIND}

\author{Dominique Gravel}
\author{Timothée Poisot}
\author{Philippe Desjardins-Proulx}

\begin{abstract}
Background: \\
Question: \\
Approach: \\
Key results: \\
Conclusion\\

\end{abstract}

\keywords{metacommunity ecology, neutral theory, species
sorting, patch dynamics, spatial networks, dispersal}

\maketitle

%========================================================%
\section{Introduction}
%DG

- Contribution of neutral theory to ecology: the recognition of
the importance of dispersal in structuring communities. Link with limnology.

@@

- Objective of the paper 
	- Already several reviews of neutral theory in the literature
- We will use this opportunity to explore in more details the
contribution of neutral theory to our understanding of
metacommunities

- We will pay a particular attention to recent developments at
the crossroad of network theory

- Move from a perspective where dispersal is either global or
spatially explicity (e.g. over a lattice), and spatial constant,
to a perspective focusing on the variance of dispersal.

- More specifically, the objective of the paper is to use
neutral theory to better reveal the importance of landscape
network structure on the distribution of diversity.
	- Referred as a "spatial contingency" 
	- Relevance to limnology

@@

%========================================================%
\section{Network representation of landscapes}
% PDP

Entités discrètes --> réseaux

@@

%========================================================%
\section{Model description}
% DG

General introduction to the section

\subsection{Patch dynamics}
blabla

\subsection{Neutral dynamics}

\subsection{Species sorting and mass effect}
blabla

%For each model:
%	- description of the dynamics
%	- description of the algorithm
%	- main predictions
blabla

%========================================================%
\section{Results}
% TP

\subsection{Alpha diversity}

\subsection{Beta diversity}

%========================================================%
\section{Discussion}
% TP

Contrasting the three perspectives: what do we learn?

New questions

Making the theory operational

Distribution attendue des espèces dans un paysage: utiliser la théorie neutre pour avoir un attendu (différents de la méthode classique de permutation)

- Déviation locale des prédictions

- Importance de la structure du paysage sur les propriétés émergentes

-

\end{document}
%========================================================%
